\newcommand{\PERSONshap}[0]{Jonathan Shapiro}
\newcommand{\PERSONscottSmith}[0]{Scott Smith}
\newcommand{\PERSONsamWeber}[0]{Samuel Weber}
\newcommand{\PERSONjustin}[0]{Justin Payne}
\newcommand{\PERSONfollis}[0]{Benjamin D. Follis}
\newcommand{\PERSONlandahl}[0]{Paul Landahl}
\newcommand{\PERSONdad}[0]{Steve Hardy}
\newcommand{\PERSONmom}[0]{Mary Lou Doerrie}
\newcommand{\PERSONben}[0]{Benjamin Hardy}
\newcommand{\PERSONnwf}[0]{Nathaniel Wesley Filardo}
\newcommand{\PERSONzach}[0]{Zachary Palmer}
\newcommand{\PERSONswaroop}[0]{Swaroop Sridhar}

\begin{acknowledgment}
  
  
  To \PERSONshap{}, my advisor, for his mentorship near and far.
  His guidance has been instrumental to the completion of this work and his encouragement has been inspirational.

  To my parents, \PERSONmom{} and \PERSONdad{}, for encouraging me to persevere and for supporting me through difficulty.
  This would not have been possible without your help.

  To Sabina Lindley, for her understanding and encouragement during many stressful days and late nights.

  To
  Harriet Doerrie,
  \PERSONmom{},
  Peggy Doerrie,
  \PERSONben{},
  \PERSONdad{},
  Dave Paxson,
  and
  Nancy Paxson, for all their love and encouragement.

  To my dissertation committee,
  \PERSONshap{},
  \PERSONscottSmith{},
  and
  \PERSONsamWeber{},
  for providing critical guidance and feedback through this process.

  I would also like to thank the many people who have helped me evolve this work:
  \PERSONnwf{},
  \PERSONfollis{},
  \PERSONlandahl{},
  Hari Menon,
  Mark S. Miller,
  Eric Northup,
  \PERSONzach{},
  \PERSONjustin{},
  Eric Perlman,
  Alex Rozenshteyn,
  \PERSONshap{},
  \PERSONscottSmith{},
  \PERSONswaroop{},
  \PERSONsamWeber{},
  and
  Charles Wright.

  For their help reviewing this dissertation, I would like to thank
  \PERSONben{},
  \PERSONnwf{},
  \PERSONzach{},
  \PERSONjustin{},
  \PERSONshap{},
  \PERSONscottSmith{},
  and
  \PERSONsamWeber{}.
  Special thanks go to \PERSONzach{} for his help with LaTeX and the Johns Hopkins dissertation formatting criteria.
  Special thanks also go to \PERSONfollis{} for his help with PDF/A-1b formatting.

  To everyone else supporting me through this effort: You are amazing!  Thank you!
  
\end{acknowledgment}


