\begin{vita}
  
  M. Scott Doerrie was born the son of \PERSONmom{} and \PERSONdad{} on October 3rd, 1979 in Robbinsdale, MN.
  After graduating from high school in 1998 from Coon Rapids, MN, he studied Computer Science at the Gustavus Adolphus College in Saint Peter, MN, where he earned his Bachelor of Arts in 2002.
  He joined the Systems Research Laboratory (SRL) as a Research Assistant at the Johns Hopkins University in 2003.

  While at SRL, he was involved in the design of both Coyotos, BitC, and \TMmodelName{}.
  He notably contributed formalisms for reasoning about on-line address-space traversal and update algorithms for the preliminary Coyotos GPT design.
  He also assisted with the development of BitC with a focus on keeping the language tractable for future analysis.
  Ultimately, his graduate research focused on \TMmodelName{}, demonstrating through automated verification that capability-based systems could enforce security policies, namely confinement.
  
  M. Scott Doerrie gained experience as an instructor while completing his doctoral research.
  As a co-instructor with \PERSONswaroop{} for three consecutive years, he designed and presented novel course material for the ``Operating Systems'' course at Johns Hopkins University.
  He also prepared a half-semester seminar for the Systems Research Laboratory on the use of the logical frameworks.

  In his doctoral thesis, M. Scott Doerrie combined multiple disciplines of Computer Science; he drew from the domains of operating systems, access control mechanisms, machine-assisted verification, safe language run-times, and advanced type systems.
  His future research interests include building and improving mechanisms to produce secure systems.
  
\end{vita}
